RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-31 discussion.tex
figure and case studies and discussion
yes

\section{Discussion, Lessons and Limitations}

@@

Experience with deploying RCloud in a community of data analysts
(hackers in the parlance of Heer and Agrawala)
has provided some insight about how the proposed requirements
were met, and to what extent they were appropriate.
This experience may be informative to researchers and designers
of future systems supporting collaborative visual analytics.

Returning to the design considerations defined by Heer and Agrawala,
our experience underscores the importance of their proposals,
and indicates areas for further exploration, especially in the
following areas.

>>>>

\section{Discussion, Lessons and Limitations}
\label{sec:limitations}

@@

Experience with deploying RCloud in a community of data analysts
(hackers in the classification of Heer and Agrawala)
has provided some insight about how the proposed requirements
were met and to what extent they were appropriate.
This experience may be informative to researchers and implementers
of future systems supporting collaborative visual analytics.

Returning to Heer and Agrawala's design considerations, our experience
both underscores the relevance of their proposals and indicates areas
for further exploration. We briefly examine these aspects of the
visual analytics environment.
